SNIK Quiz: A Multiple Choice Game about Information Management in Hospitals

### 2022-03-17 paper.tex
More revision.

This paper presents SNIK Quiz, an open source\footnotemark{} browser game, see \cref{fig:snikquiz}, in which students answer multiple-choice questions about HIM, including an evaluation by domain experts and a student.

@@

The main limitation of SNIK Quiz is that qualitative feedback on those complex questions is mixed.
One of the experts questioned the didactic value of the \emph{intertwined} questions, as the users cannot know the exact graph structure of SNIK and thus may difficulties deciding, which triplets of concepts are most strongly connected.
While the closeMatch were rated as most complex, the complexity was seen mostly seen as grammatical and not enough on the didactically relevant relationships between the entities.
Contrary to the initial assumption that well explained questions would be beneficial, shorter questions were preferred as they could be read more quickly.
\todo{distractors}
%Distractor generation using graph neighbourhood suffers from the meta model of SNIK, where 
%Generally,

\todo{subklassenbeziehung bei nachbarschaft problematisch, weil implizit relation für die auch gilt, oberklassen sind ok, weil es nicht auf alle zutrifft. auf beispiel mit physician und senior physician und healthcare professional verweisen.}
\todo{enge nachbarschaft allgemein problematisch, weil die relationen dann so ungefähr mit gelten}
\todo{wir brauchen benannte abkürzungen wie großeltern = kind->kind}
\todo{momentan für studenten nicht verwendbar und für prüfungen schon gar nicht, muss für praktischen einsatz noch weiter ausgebaut werden}
\todo{gibt auch rückschlüsse auf fehler der ontologie und hilft uns herauszufinden, was wirklich gemeint ist. auch wichtig mit some vs forall quantor und so.}

@@

%\section{Future Work}
\section{Conclusions}
SNIK Quiz shows that knowledge on the management of information systems in medicine and health care can be used to semi-automatically generate multiple-choice questions.
While preliminary evaluations show promising results, the complex question types need to be investigated further.
Future work should also include a quantitative evaluation of learning efficiency when supplementing courses with SNIK Quiz.
%Use of neural networks and language models in combination with linked data to generate more natural questions and answers is another avenue for further exploration.

>>>>

This paper presents SNIK Quiz, an open source\footnotemark{} browser game, see \cref{fig:snikquiz}, in which students answer multiple-choice questions about health information management (HIM), including an evaluation by domain experts and a student.

@@

The main limitation of SNIK Quiz is that qualitative feedback on those complex questions is mixed.
One of the experts questioned the didactic value of the \emph{intertwined} questions, as the users cannot know the exact graph structure of SNIK and thus may difficulties deciding, which triplets of concepts are most strongly connected.
While the closeMatch were rated as most complex, the complexity was seen mostly seen as grammatical and not enough on the didactically relevant relationships between the entities.
Contrary to the initial assumption that well explained questions would be beneficial, shorter questions were preferred as they could be read more quickly.
%A limitation of the distractor generation using graph neighbourhood is that it includes subclass/superclass relationships, where it is not clear whether the given wrong answer can be argued to hold as well, even if that fact is not explicitly modelled.
Questions should also clarify that the least specific correct answer is expected in cases such as the example for the subject template in \cref{tab:templates}:
As a subclass of the correct answer \enquote{physician}, each \enquote{senior physician} is also implicitly responsible for medical admission and for \enquote{health care professionals} (superclass of physician) this is at least partly true.
As SNIK can only cover the domain of HIM as far as it is described by the underlying textbooks, distractors may actually be correct answers in the real world.
Evaluation of SNIK Quiz questions helps uncover and fix missing and incorrect facts in SNIK.
%Generally, close neighbourhood is problematic for distractor generation in SNIK because, .
%It needs to be investigated further, whether subclass relationships should be excluded in future work or whether provide valuable distractors.
% SeniorPhysician < Physician < HealthCareProfessional
%Distractor generation using graph neighbourhood suffers from the meta model of SNIK, where 
%Generally,

%\todo{enge nachbarschaft allgemein problematisch, weil die relationen dann so ungefähr mit gelten}
%\todo{wir brauchen benannte abkürzungen wie großeltern = kind->kind}
%\todo{gibt auch rückschlüsse auf fehler der ontologie und hilft uns herauszufinden, was wirklich gemeint ist. auch wichtig mit some vs forall quantor und so.}

@@

%\section{Future Work}
\section{Conclusions}
SNIK Quiz shows that knowledge on the management of information systems in medicine and health care can be used to semi-automatically generate multiple-choice questions.
While preliminary evaluations show promising results, the complex question types need to be investigated further before it can be effectively used by students.
Future work should also include a quantitative evaluation of learning efficiency when supplementing courses with SNIK Quiz.
%Use of neural networks and language models in combination with linked data to generate more natural questions and answers is another avenue for further exploration.
